Parsing Postfix log files

### 2009-04-04 doc/logparser-implementation.tex
Added graph showing number of action invocations, excluding log files 22 and 62-68. Removed table and old action invocations graph. Removed old discussion of number of action invocations, and wrote a new one referring to the new graph.

XXX RUN test-some, STITCH THE COUNTS OF NUMBER OF RULES INVOKED INTO THE
REAL TIMING DATA, UPDATE THE NUMBER OF INVOCATIONS GRAPH, AND WRITE ABOUT
IT\@.

\parsernames{} actions are described in detail in \sectionref{actions in
detail in implementation}, and \sectionref{adding new actions in
implementation} covers the process of adding a new action.

\showgraph{build/graph-action-distribution}{Distribution of rules per
action}{Distribution of rules per action}

\showgraph{build/graph-number-of-action-invocations}{Number of times each
action was invoked when parsing \numberOFlogFILES{} log files}{Number of times
each action was invoked}

>>>>

There is no correlation between how often an action is specified by rules
and how often an action is invoked because a rule recognises a log line.
\Graphref{Number of times each action was invoked excluding 22 and 62--68}
shows the number of times each action was invoked when parsing the
\numberOFlogFILES{} log files used to generate the statistics in
\sectionref{parser efficiency}, \textit{excluding\/} log files 22 and
62--68, because their content is extremely skewed by two mail loops (see
\sectionref{Explaining the peaks in log file size}).  The action most
commonly specified by rules, \action{DELIVERY\_REJECTED}, is the third most
commonly invoked action; the most commonly invoked actions,
\action{CONNECT} and \action{DISCONNECT}, are each specified by only one
rule.  The \action{UNINTERESTING} action, the third most commonly specified
action, is halfway down the graph.

As expected, some actions have been invoked almost exactly the same number
of times: almost every \action{CONNECT} will have a \action{DISCONNECT},
and there is only a 0.00042\% difference between the number of times the
two were invoked; every mail that enters Postfix's queue will be managed by
\daemon{qmgr} (\action{MAIL\_QUEUED}) and processed by \daemon{cleanup}
(\action{CLEANUP\_PROCESSING}), and again there is only a 0.01648\%
difference between their invocations.  Confusingly,
\action{CLEANUP\_PROCESSING} is invoked more often than
\action{MAIL\_QUEUED}: occasionally, accepted mail in the process of being
transferred is interrupted by a timeout, and there is a log line from
\daemon{cleanup} but not from \daemon{qmgr}, as described in
\sectionref{discarding cleanup log lines}.

\showgraph{build/graph-action-distribution}{Number of rules specifying each
action}{Distribution of rules per action}

\showgraph{build/graph-number-of-action-invocations-excluding-22-and-62--68}{Number
of times each action was invoked when parsing \numberOFlogFILES{} log
files, excluding log files 22 and 62--68}{Number of times each action was
invoked excluding 22 and 62--68}
